\section{\texorpdfstring{$\Upsilon$}{Y} signal extraction}
\label{sec:upsilon}

%% ============================================================================
\subsection{Selection}
\label{sec:ups:selelection}

The data sample used in this analysis has been collected by \lhcb in 2011 and
2012, at center-of-mass energies of \sqs=7\tev and 8\tev with corresponding
integrated luminosities  1089\invpb and 2011\invpb.
The pre-selected event candidates were taken from microDST dedicated to
quarkonia studies (WGBandQSelection4-1) that was processed using a 
stripping lines Stripping20r1 for 2011 data and Stripping20 for 2012 data.

%% ============================================================================
\subsubsection{Pre-selection}
\label{sec:upsilon:selelection:preselection}

The selection starts by forming candidates from pairs of oppositely-charged
tracks identified as muons and originated from a common vertex.
Good track quality is ensured by requiring a $\chisq$ per degree of
freedom ($\chisq/\rm{ndf}$) to be less then 4 for the track fit and primary
vertex probability greater than 0.5 \%.
The muons were required to have a transverse momentum higher than 1 \gev.
To suppress  duplicate tracks  a the cut on Kullback-Leibler (KL)
distance~\cite{Needham:1082460} was used: only tracks with symmetrized KL distance less
than 5000 were selected.
The primary vertex of dimuon candidate is required to be within luminous region
defined as $|z_{PV}| < 0.5 m$ and $x_{PV}^2 + y_{PV}^2 < 100 mm^2$.

%% ============================================================================
\subsubsection{Trigger}
\label{sec:upsilon:selection:trigger}

For Upsilon studies the event candidates  were required to trigger by three
trigger levels ('TOS' requirement). The first level is L0DiMuon which  requires
two muon candidates with their $p_T$ product larger than 1.68 \gevcc and
a relaxed SPD requirement (less then 9000 SPD hits).

The second level is HLT1 trigger where the event candidates were required to
pass the Hlt1DiMuonHighMass line.
This line triggers events with  two well reconstructed tracks  which have hits
in the muon system  that have a transverse momentum higher that 500 \mevc and 
a total momentum higher that 6 \gevc that produced from a common vertex with
invariant mass higher than 2.7 \gevcc.

At the last HLT2 level the event need to be accepted by the HLT2DiMuonB line.
This line confirms the HLT1 decision and requires the invariant mass of the
dimuon pair to be larger than 4.7 \gevcc.

%% ============================================================================
\subsubsection{This study selection}
\label{sec:upsilon:selection:study}

To improve the muon identification purity two additional cuts are used. The
first one is applied on the difference in logarithm of the likelihood of the
muon and hadron hypotheses~\cite{Powell} provided by the muon detection system.
This difference ($\Delta\log\lum^{\mmu-\Ph}$) should be greater than 0. The
second selection  is a cut on the muon probability value obtained from a Neural
Network algorithm (ProbNN). This algorithm takes in account the various
reconstruction information such as the RICH particle identification, the muon
quality reconstruction and compatibility with a minimum ionising particle in the
calorimeters. In this study selected events requiring to have the ProbNN value
greater than $0.5$.

The criteria for  $\Upsilon$ selection are summarized in
Table~\ref{tab:upsilon:selection:study:summary}.

\input{tables/upsilon/selection_study_summary}

%% ============================================================================
\subsection{Fit model}
\label{sec:upsilon:fit}
To determine the $\Upsilon$ meson signal yields, an unbinned maximum likelihood
fit to dimuon mass distribution has been performed. The signals have been
modeled with the sum of three CrystalBall (CB) functions and an exponential
function for the combinatorial background. Each of the CrystalBall functions
corresponds to \Y1S, \Y2S and \Y3S signals and can be written in the following
form:

\begin{equation}
CB(x) = N \times
\begin{cases}
\frac{1}{\sqrt{2\pi\sigma}}\exp(-\frac{(x-\mu)^2}{2\sigma^2}) & \text{, if $\frac{x-\mu}{\sigma} > -\alpha$} \\
\frac{1}{\sqrt{2\pi\sigma}}(\frac{n}{|\alpha|})^n \exp(-\frac{|\alpha|^2}{2})(\frac{n}{|\alpha|}-|\alpha|-\frac{x-\mu}{\sigma})^{-n} & \text{, otherwise}
\end{cases}
\label{eq:cb}
\end{equation}

The CB is similar to gaussian distribution, but has an asymmetric tail. This
function has five parameters: N, $\mu$, $\sigma$, $\alpha$ and $n$, where
parameters $\mu$ and $\sigma$ have the same meaning as for gaussian. Parameters
$\alpha$ and $n$ describe the tail behavior: $\alpha$ controls the tail start
and $n$ corresponds to the decreasing power of the tail. All three parameters
$N$, $\alpha$ and $n$ contribute to the amplitude.

The mass of \Y1S is allowed to vary. Mass of \Y2S (\Y3S) are defined as sum of
\Y1S mass and the value of corresponding difference between mass of
\Y2S (\Y3S) and \Y1S. These two mass differences, named $\Delta m_{\Y2S}$ and
$\Delta m_{\Y3S}$, are fixed in the fit to 563 \mevcc and 895 \mevcc
correspondingly.

The width of the Crystal Ball function describing the \Y1S meson is allowed to
vary, while the width of \Y2S and \Y3S mesons are constrained to the value of
the width of the \Y1S signal, scaled by the ratio of the masses of \Y2S and \Y3S
to the \Y1S meson.

The  $\alpha$ and $n$ parameters are fixed to the values found in
the simulation studies.
The $\alpha$ value is fixed to 2 and $n$ value is fixed to 1 in each of three
CB functions.

%% ============================================================================
\subsection{Fit results}
\label{sec:upsilon:result}

Figure~\ref{fig:upsilon:result:nominal} presents the result of the fit that is
described in the previous section. Fit was performed in the dimuon
transverse momentum interval $ 6 < p_T^{\mumu} < 40 \gevc$.
Table~\ref{tab:upsilon:result:nominal} shows the parameters values of this fit.

\input{pics/upsilon/result_nominal}
\input{tables/upsilon/result_nominal}

\input{pics/upsilon/mean_sigma}

Table~\ref{tab:upsilon:result:nominal} shows the fitted \Y1S mass is about
5 \mevcc lower than PDG value $9460.30 \pm  0.26$ \mevcc.

% \input{upsilon/result/pics/mass}


To obtain the final numbers for $\Upsilon$ yields the fit was repeated
independently for each of the $p_T^{\mumu}$ bins with the \OneS mass 
fixed to $9.456 \gevcc$ that was measured in the fit of joined 2011 and 2012
datasets.

Figure~\ref{fig:upsilon:result:yields} shows the number of signal events as
function of dimuon transverse momentum.
Table~\ref{tab:upsilon:result:fits} in Appendix summarizes the obtained results.

\input{pics/upsilon/result_yields}


% \input{upsilon/selection/index}
% \input{upsilon/fit/index}
% \input{upsilon/result/index}